Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-02 sattose/paper.tex
I want to say something about the redefinitions in the abstract, but I don't know how.
I don't like this sentence

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code. There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately a fifth of the duplication can be refactored through method extraction, the other clones require other techniques to be applied. More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones. As the desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems. This model will be implemented for the Java programming language.
\end{abstract}

@@

For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. The tool will be developed on GitHub and stored in the Software Heritage \cite{di2017software} archives to ensure long term preservation. This way we strive to make the problem of duplication in source code easier to deal with.

>>>>

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code. There are several techniques that can be used in order to merge clones, reduce duplication, improve the design of the code and potentially also reduce the total volume of a software system. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. We look into redefinitions for different types of clones that have been used in code duplication research for many years. These redefinitions are aimed towards flagging only clones that are useful for refactoring purposes. Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. Approximately a fifth of the duplication can be refactored through method extraction, the other clones require other techniques to be applied. More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones. As the desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems. This model will be implemented for the Java programming language.
\end{abstract}

@@

For this research, we strive to improve upon the current state-of-the-art in clone refactoring by building a clone refactoring tool that applies refactorings to a large percentage of clones found. The design decisions for this tool will be made on basis of data gathered from a large corpus of software systems. This way we strive to make the problem of duplication in source code easier to deal with.
